Response to the defense feedback

### 2021-06-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

\chapter{Introduction} \label{chapter1}
Software is becoming increasingly complex today. Half a century ago, the Appollo 11's flight software~\cite{hamilton19690apollo} was done with around 100,000 lines of code. 
Today, a mobile application such as Telegram~\cite{telegram} contains more than 2,000,000 lines of code. It is estimated that engineers built Google's infrastructure with 2 billion lines of code~\cite{potvin2016google}. The complexity in today's software systems makes it hard for software developers to understand the codebase and find defects manually. So an automated bug detection tool is often needed. In this dissertation, we present techniques to analyze side-channel vulnerabilities in real-world applications. The side-channel vulnerability is a type of information leakage bug in software systems. Unlike many ordinary bugs, attackers can exploit side-channel vulnerabilities from the implementation of the software with various different methods rather than the weaknesses of the software. So it is sometimes harder for developers to reason about these vulnerabilities.

>>>>

\chapter{Introduction} \label{chapter1}
Software is becoming increasingly complex nowadays. Half a century ago, the Appollo 11's flight system software~\cite{hamilton19690apollo} was done with around 100,000 lines of code. 
Today, a mobile application such as Telegram~\cite{telegram} contains more than 2,000,000 lines of code. It is estimated that engineers built Google's infrastructure with 2 billion lines of code~\cite{potvin2016google}. The complexity in today's software systems makes it hard for software developers to understand the codebase and find defects manually. So an automated bug detection tool is often needed. In this dissertation, we present techniques to analyze side-channel vulnerabilities in real-world applications. The side-channel vulnerability is a type of information leakage bug in software systems. Unlike many ordinary bugs, attackers can exploit side-channel vulnerabilities from the implementation of the software with various different methods rather than the weaknesses of the software. So it is sometimes harder for developers to reason about these vulnerabilities.
